\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/background.tex

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
D-). The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers USB packets.

>>>>

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
D-). The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers USB packets.

### 2021-01-30 WOOT/Files/conclusion.tex

Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The scripting mode largely extends the
original BadUSB and successfully bypasses existing defenses. The privacy
extraction mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The remote control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different mode and proves it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

>>>>

Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The HID Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different mode and proves it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

\section{Responsive Disclosure}

Responsive disclosure have already been carried out, we have already contacted the affected vendors through proper channel and are waiting for mitigation being deployed.
